### 2014-11-08 tex/precise.tex
adding moi changes

Consider the graph shown in~\figref{fig:fHeap}(b) the reference
$r_2^i$ is created during the initialization of $\mathit{this}.y$. The
reference that is returned during the access of the field, however, is
$r_3^s$. The reference $r_3^s$ points to the value set of $r_2^i$
which are: $(\phi_{2a}, l_\mathit{null})$, $(\phi_{2b}, l_2)$, and
$(\phi_{2c}, l_1)$. The values of the constraints $\phi_{2a}$,
$\phi{2b}$, and $\phi_{2c}$ are defined in~\figref{fig:initHeap}(d).

@@

@@

@@

\begin{figure*}
\begin{tabular}[c]{cl}
\usebox{\boxPEQ} & \usebox{\boxPEX} \\ \\
(a) & (b) \\
\end{tabular}
\caption{equals true for this.x == this.y}
\label{fig:eqs-true}
\end{figure*}

>>>>

Consider the graph shown in~\figref{fig:fHeap}(b) the reference
$r_2^i$ is created during the initialization of $\mathit{this}.y$. The
reference that is returned during the access of the field, however, is
$r_3^s$. The reference $r_3^s$ points to the value set of $r_2^i$
which are: $(\phi_{2a}, l_\mathit{null})$, $(\phi_{2b}, l_2)$, and
$(\phi_{2c}, l_1)$. The values of the constraints $\phi_{2a}$,
$\phi_{2b}$, and $\phi_{2c}$ are defined in~\figref{fig:initHeap}(d).

@@

The reference $r_x$ is the base pointer whose field is being written
to while $r$ is the target reference. We look up the value of the base
reference in the environment $\eta(x)$. The set $\Psi_x$ is the set of
tuples of constraints, locations, and references which provide the
reference chains leading from $r_x$ to the reference of the field,
$r_\mathit{curr}$, being written to through $\phi$ and $l$.The goal is
to overwrite the $r_\mathit{curr}$ references with the target
references. Since the target of the write is $r$, we first check that the
location constraint pairs of $L(r)$ are satisfiable when accessed
through the $r_x$ chain. This is accomplished by the strengthing
function.

@@

Additionally, we also check for conditions where the write is not possible

@@

\begin{figure*}
\begin{tabular}[c]{cl}
\usebox{\boxPEQ} & \usebox{\boxPEX} \\ \\
(a) & (b) \\
\end{tabular}
\caption{equals true for this.x == this.y}
\label{fig:eqs}
\end{figure*}

The rewrite rules for check the equals true and equals false when
comparing two references in the symbolic summary heap is shown
in~\figref{fig:eqs}(a). First the equals reference true rewrite rule
returns true if two references $r_0$ and $r_1$ are equal. In GSE this
is a simple comparision of object refrences. In the symbolic summary
heap, however, there we campare sets of constraint location pairs for
each reference. We construct three sets of constraints (i)
$\Phi_\alpha$ constains combinations of constraints ($\phi_0 \wedge
\phi_1$) from $r_0$ and $r_1$
